---
title: 'Study 2: Data preparation'
output: pdf_document
  keep_md: true
---

This R markdown provides the data preparation for our CogSci proceedings paper (Jansen, Paxton, Krafft, Lombrozo, & Griffiths, *in preparation*).

To run this from scratch, you will need the following files:

* `./data-experiment/cleaned_data/joined_data.csv`: Merged summary and questionnaire data from Dallinger study, cleaned by P. Krafft (see code on GitHub). Available for download: https://osf.io/u7jyk/
* `./data-ratings/`: Directory with ratings of the first and last summary in each transmission chain (coded by R. Jansen and P. Krafft).
* `./supplementary-code/`: Directory with functions and libraries needed to run this code.

**Code written by**: A. Paxton (University of California, Berkeley)

**Date last modified**: 1 Feb 2018

***

# Data preparation: Questionnaires

***

## Preliminaries

```{r prep-questionnaires, warning = FALSE, error = FALSE, message = FALSE}

# clear our workspace
rm(list=ls())

# read in libraries and create functions
source('./supplementary-code/required_packages-sim.r')
source('./supplementary-code/libraries_and_functions-sim.r')

```

## Expand questionnaire file

```{r read-questionnaire}

# expand stringified JSON of questions
questionnaire_file = read_csv('./data-experiment/cleaned_data/joined_data.csv') %>%
  cbind(., jsonlite::stream_in(textConnection(.$survey))) %>%
  select(-survey,-X1)

```

## Export to new file

```{r export-expanded-questionnaire}

write.table(questionnaire_file, './data-experiment/cleaned_data/sim-expanded_questionnaire.csv', 
            sep=',', append = FALSE, quote = FALSE, row.names = FALSE, col.names = TRUE)

```


***

# Data prepartion: Ratings

***

## Preliminaries

```{r prep-ratings, warning = FALSE, error = FALSE, message = FALSE}

# clear our workspace
rm(list=ls())

# read in libraries and create functions
source('./supplementary-code/required_packages-sim.r')
source('./supplementary-code/libraries_and_functions-sim.r')

```

## Concatenate ratings files

```{r concatenate-ratings, warning = FALSE, error = FALSE, message = FALSE}

# get list of individual experiments included in the data
rating_files = list.files('./data-ratings', recursive=FALSE)

# concatenate the files
vector_files = data.frame()
info_files = data.frame()
questionnaire_files = data.frame()
node_files = data.frame()
participant_files = data.frame()


for (rating_file in rating_files){
  
  # read in the next file and get metadata
  file_info = strsplit(file_path_sans_ext(as.character(rating_file)),"_|-")
  rater_id = trim.spaces(file_info[[1]][2])
  topic_name = trim.spaces(file_info[[1]][3])
  
  x = read_csv(paste('./data-ratings/',rating_file,sep=''))

  # read in vector file
  next_vector = read_csv(paste(experiment,'/vector.csv',sep='')) %>% 
    mutate(experiment = exp_id) %>%
    mutate(code_version = code_version) %>%
    mutate(story_num = story_num) %>%
    mutate(rep = rep) %>%
    select(-contains('property'),-one_of(unneeded_vars)) %>%
    dplyr::filter(origin_id != 1)
  
  # read in info
  next_info = read_csv(paste(experiment,'/info.csv',sep='')) %>% 
    mutate(experiment = exp_id) %>%
    mutate(code_version = code_version) %>%
    mutate(story_num = story_num) %>%
    mutate(rep = rep) %>%
    select(-contains('property'),-one_of(unneeded_vars)) %>%
    rename(summary = contents) %>%
    dplyr::filter(origin_id != 1)
  
  # read in questionnaire
  next_q = read_csv(paste(experiment,'/question.csv',sep='')) %>% 
    mutate(experiment = exp_id) %>%
    mutate(code_version = code_version) %>%
    mutate(story_num = story_num) %>%
    mutate(rep = rep) %>%
    select(-contains('property'),-one_of(unneeded_vars))
  
  # read in node information
  next_node = read_csv(paste(experiment,'/node.csv',sep='')) %>% 
    mutate(experiment = exp_id) %>%
    mutate(code_version = code_version) %>%
    mutate(story_num = story_num) %>%
    mutate(rep = rep) %>%
    select(-contains('property'),-one_of(unneeded_vars)) %>%
    na.omit()
  
  # read in participant information
  next_participant = read_csv(paste(experiment,'/participant.csv',sep='')) %>% 
    mutate(experiment = exp_id) %>%
    mutate(code_version = code_version) %>%
    mutate(story_num = story_num) %>%
    mutate(rep = rep) %>%
    dplyr::filter(status=='approved') %>%
    select(-contains('property'),
           -status,
           -one_of(unneeded_vars))

  # append to group files
  vector_files = rbind.data.frame(vector_files, next_vector)
  info_files = rbind.data.frame(info_files, next_info)
  questionnaire_files = rbind.data.frame(questionnaire_files, next_q)
  node_files = rbind.data.frame(node_files, next_node)
  participant_files = rbind.data.frame(participant_files, next_participant)

}

# clean up
rm(next_info, next_node, next_participant, next_q, next_vector)

```

## Read in questionnaire data

```{r expand-questionnaire}

# clean up questionnaire data by converting the stringified JSONs to a new variable
questionnaire_files = questionnaire_files %>% ungroup() %>%
  select(experiment, participant_id, response, code_version, rep, story_num) %>%
  cbind(., jsonlite::stream_in(textConnection(.$response))) %>%
  select(-response)

```

## Export lightly cleaned data

```{r export-lightly-cleaned-data}

write.table(vector_files, './data/vector_files.csv', 
            sep=',', append = FALSE, quote = FALSE, row.names = FALSE, col.names = TRUE)

write.table(info_files, './data/info_files.csv', 
            sep=',', append = FALSE, quote = FALSE, row.names = FALSE, col.names = TRUE)

write.table(questionnaire_files, './data/questionnaire_files.csv', 
            sep=',', append = FALSE, quote = FALSE, row.names = FALSE, col.names = TRUE)

write.table(node_files, './data/node_files.csv', 
            sep=',', append = FALSE, quote = FALSE, row.names = FALSE, col.names = TRUE)

write.table(participant_files, './data/participant_files.csv', 
            sep=',', append = FALSE, quote = FALSE, row.names = FALSE, col.names = TRUE)

```

## Combine into master dataframe

```{r}

x = full_join(questionnaire_files,
  mutate(info_files, origin_id=origin_id-1), 
              
              by=c('experiment',
                   'code_version',
                   'rep',
                   'story_num',
                   'participant_id' = 'origin_id'))
  
#   
#   # bring in the questionnaire data
#   full_join(.,
#             questionnaire_files,
#             by = c('worker_id' = 'participant_id',
#                    'experiment',
#                    'code_version',
#                    'rep',
#                    'story_num')) %>%
#   
#   # bring in the node information
#   full_join(.,
#             node_files,
#             by=c('experiment',
#                    'code_version',
#                    'rep',
#                    'story_num',
#                    'worker_id' = 'participant_id')) %>%
#   
#   full_join(.,
#            mutate(info_files,origin_id=origin_id-1),
#             by=c('experiment',
#                    'code_version',
#                    'rep',
#                    'story_num',
#                    'worker_id' = 'origin_id')) 
#   
#   
#   
#   full_join(node_files,
#               participant_files,
#               by=c('experiment',
#                    'code_version',
#                    'rep',
#                    'story_num',
#                    'participant_id' = 'worker_id')) %>%
#   dplyr::filter(status == 'approved') %>%
#   select(-status) %>%
#   full_join(.,
#             mutate(info_files,origin_id=origin_id-1),
#             by=c('experiment',
#                    'code_version',
#                    'rep',
#                    'story_num',
#                    'participant_id' = 'origin_id')) %>%
#   na.omit() %>%
#   full_join(.,
#             questionnaire_files)

```

## Create unique participant identifiers across experiments

```{r}



```

