---
title: 'Study 2: Data preparation'
output: pdf_document
  keep_md: true
---

This R markdown provides the data preparation for our CogSci proceedings paper (Jansen, Paxton, Krafft, Lombrozo, & Griffiths, *in preparation*).

To run this from scratch, you will need the following files:

* `./data-experiment/cleaned_data/joined_data.csv`: Merged summary and questionnaire data from Dallinger study, cleaned by P. Krafft (see code on GitHub). Available for download: https://osf.io/u7jyk/
* `./data-ratings/`: Directory with ratings of the first and last summary in each transmission chain (coded by R. Jansen and P. Krafft).
* `./supplementary-code/`: Directory with functions and libraries needed to run this code.

**Code written by**: A. Paxton (University of California, Berkeley)

**Date last modified**: 1 Feb 2018

***

# Data preparation: Questionnaires

***

## Preliminaries

```{r prep-questionnaires, warning = FALSE, error = FALSE, message = FALSE}

# clear our workspace
rm(list=ls())

# read in libraries and create functions
source('./supplementary-code/required_packages-sim.r')
source('./supplementary-code/libraries_and_functions-sim.r')

```

## Expand questionnaire file

```{r read-questionnaire}

# expand stringified JSON of questions
questionnaire_file = read_csv('./data-experiment/cleaned_data/joined_data.csv') %>%
  cbind(., jsonlite::stream_in(textConnection(.$survey))) %>%
  select(-survey,-X1)

```

## Export to new file

```{r export-expanded-questionnaire}

write.table(questionnaire_file, './data-experiment/cleaned_data/sim-expanded_questionnaire.csv', 
            na = "-999999999",
            row.names = FALSE,
            col.names = TRUE,
            sep = "\t")

```


***

# Data prepartion: Ratings

***

## Preliminaries

```{r prep-ratings, warning = FALSE, error = FALSE, message = FALSE}

# clear our workspace
rm(list=ls())

# read in libraries and create functions
source('./supplementary-code/required_packages-sim.r')
source('./supplementary-code/libraries_and_functions-sim.r')

```

## Concatenate ratings files

```{r concatenate-ratings, warning = FALSE, error = FALSE, message = FALSE}

# get list of individual experiments included in the data
rating_files = list.files('./data-ratings', recursive=FALSE)

for (rating_file in rating_files){
  
  # read in the next file and get metadata
  file_info = strsplit(file_path_sans_ext(as.character(rating_file)),"_|-")
  rater_id = trim.spaces(file_info[[1]][2])
  topic_name = trim.spaces(file_info[[1]][3])
  
  # read in rating dataframe
  rating_df = read_csv(paste('./data-ratings/',rating_file,sep=''))

}


```
